Implicit neural representation of potential fields

### 2024-06-02 manuscript.tex
Add header and chapter numbers to sections
De-number authorship declaration because including signed pdf copy, fixes TOC page length
Adjust chapter titles
Prompted by reviewer 2 to better present the thesis

\pagenumbering{arabic}
\setcounter{page}{1}
\setcounter{section}{0}
\renewcommand{\thesection}{\arabic{section}}

\chapter{Introduction}
\label{ch:intro}
% \newrefsection{}
\input{intro}

\chapter[Magnetic Grid Resolution Enhancement Using ML]{Magnetic Grid Resolution Enhancement Using Machine Learning}
\label{ch:paper1}
% \newrefsection{}
This chapter has been reproduced from the following peer reviewed publication. Formatting has been adjusted for consistency.

@@

\chapter{Super-resolution of Aeromagnetic Survey Data}
\label{ch:paper2}
% \newrefsection{}
\input{paper2}

\chapter{Implicit Neural Representation for Potential Field Geophysics}
\label{ch:paper3}
% \newrefsection{}
\input{paper3}

>>>>

\pagenumbering{arabic}
\setcounter{page}{1}
\setcounter{section}{0}
% \renewcommand{\thesection}{\arabic{section}}

\newpagestyle{body}{
    \headrule
    \sethead[][][]{}{\textsc{\thesection}\ --- \sectiontitle}{}
    \setfoot[][][]{}{\thepage}{}
}

\pagestyle{body}
\chapter{Introduction}
\label{ch:intro}
% \newrefsection{}
\input{intro}

% \chapter[Magnetic Grid Resolution Enhancement Using ML]{Magnetic Grid Resolution Enhancement Using Machine Learning}
\chapter{Super-resolution for enhancing magnetic grids}
\label{ch:paper1}
% \newrefsection{}
This chapter has been reproduced from the following peer reviewed publication. Formatting has been adjusted for consistency.

@@

% \chapter{Super-resolution of Aeromagnetic Survey Data}
\chapter[Fine-tuning SR for real-world aeromagnetic surveys]{Fine-tuning super-resolution for real-world aeromagnetic surveys}
\label{ch:paper2}
% \newrefsection{}
\input{paper2}

% \chapter{Implicit Neural Representation for Potential Field Geophysics}
\chapter[Implicit neural representation of potential fields]{Implicit neural representation of potential fields}
\label{ch:paper3}
% \newrefsection{}
\input{paper3}

### 2024-06-02 paper3.tex
Adjust chapter titles
Prompted by reviewer 2 to better present the thesis

\title{Implicit Neural Representation for Potential Field Geophysics}
\author[1*]{Luke Thomas Smith}
\author[1]{Tom Horrocks}
\author[2]{Naveed Akhtar}
\author[1]{Eun-Jung Holden}
\author[1]{Daniel Wedge}
\affil{Centre for Data-Driven Geoscience, School of Earth Sciences, The University of Western Australia (M006), 35 Stirling Highway, 6009 Perth, Australia}
\affil{Department of Computer Science and Software Engineering, The University of Western Australia (M002), 35 Stirling Highway, 6009 Perth, Australia}
\date{\today}
% \maketitle{}

\begin{abstract}
    The recent use of spatial coordinate features in multilayer perceptron (MLP) neural networks provides opportunities for novel applications in potential field geophysics.
    So-called coordinate MLP networks allow for learning a representative function of potential fields from their surveyed samples.
    % Using this new paradigm of encoding spatial information within a neural network enables new methods for working with potential field survey data.
    We present a novel method for implicit neural representation of potential fields, demonstrate the quality of the learned implicit function by encoding real airborne geophysical survey line data, predict constant level grids, and compare the result to grid data processed with a traditional workflow.
    We further demonstrate the analytical calculation of gradients directly in the continuous domain using automatic differentiation, with the same framework used to train the neural network representation.
    Level grids queried from the learned representation closely match the reference grid product, with a peak signal to noise ratio of 40 dB.
    Horizontal gradients calculated with this method are accurate against numerically derived gradients, while the vertical gradient is a poor match.
    The training process is rapid, and only requires recorded samples from a single survey extent.
\end{abstract}

>>>>

\title{Implicit neural representation of potential fields}
\author[1*]{Luke Thomas Smith}
\author[1]{Tom Horrocks}
\author[2]{Naveed Akhtar}
\author[1]{Eun-Jung Holden}
\author[1]{Daniel Wedge}
\affil{Centre for Data-Driven Geoscience, School of Earth Sciences, The University of Western Australia (M006), 35 Stirling Highway, 6009 Perth, Australia}
\affil{Department of Computer Science and Software Engineering, The University of Western Australia (M002), 35 Stirling Highway, 6009 Perth, Australia}
\date{\today}
% \maketitle{}

\begin{abstract}
    The recent use of spatial coordinate features in multilayer perceptron (MLP) neural networks provides opportunities for novel applications in potential field geophysics.
    So-called coordinate MLP networks allow for learning a representative function of potential fields from their surveyed samples.
    % Using this new paradigm of encoding spatial information within a neural network enables new methods for working with potential field survey data.
    We present a novel method for implicit neural representation (INR) of potential fields, demonstrate the quality of the learned implicit function by encoding real airborne geophysical survey line data, predict constant level grids, and compare the result to grid data processed with a traditional workflow.
    We further demonstrate the analytical calculation of gradients directly in the continuous domain using automatic differentiation, with the same framework used to train the neural network representation.
    Level grids queried from the learned representation closely match the reference grid product, with a peak signal to noise ratio of 40 dB.
    Horizontal gradients calculated with this method are accurate against numerically derived gradients, while the vertical gradient is a poor match.
    The training process is rapid, and only requires recorded samples from a single survey extent.
\end{abstract}
